---
title: "Interactive Vis"
author: "Ciaran Miller"
date: "18/11/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


## Libraries
*** 

Let's load some libraries needed
```{r, warning=FALSE, message=FALSE }
# Libraries
library(tidyverse)   # includes ggplot2
library(hrbrthemes)  # better chart appearance
library(viridis)     # better color palette
library(plotly)      # interactive charts
library(partykit)    # includes analysis for conditional inference trees
```

## Data wrangling
*** 

Load all the data we are going to look at - in this case all back rows through testing in the last 5 years, completing both CMJ, reactive strength & speed testing.

A rough summary of the data can be viewed below:

```{r}
back_row_data <- read.csv("data/data.csv")

head(back_row_data)
```


## Let's build a chart
*** 

It's nice to see the data visually to get a hold on what it contains, in this case it might be interesting to look at whether relative peak power output, measured by CMJ, has any correlation to 10m sprint time.

We can make this interactive, so the data can be further explored.

```{r}
# Interactive scatter plot - PPO vs 10m Sprint
p <- back_row_data %>%
  mutate(text = paste("Name: ", name, "\nBody Weight (KG): ", body_weight, "\nPeak Power (W): ", peak_power, sep = "")) %>%
  ggplot( aes(x = rel_power, y = time_10, text = text)) +
  geom_point(alpha = 0.7) +
  theme_ipsum() +
  theme(legend.position = "none")
ggplotly(p, tooltip = "text")
```

## Further exploration

Relative power output also nicely predicts which speed band athletes will fall into:

```{r, results = FALSE}
## conditional inference tree on max velocity using relative power
max_v <- back_row_data$max_v

cut(max_v, 3, include_lowest = T, labels = c("Slow", "Average", "Fast"))

back_row_data <- back_row_data %>%
  mutate(
    speed = cut(time_10, 3, include_lowest = T, labels = c("Fast", "Medium", "Slow"))
  )

ctree_formula <- speed ~ rel_power

speed_ctree <- ctree(ctree_formula, data = back_row_data)

plot(speed_ctree)
````